---
title: "Country entropy"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Country entropy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 6,
  fig.width = 6, 
  comment = "#>"
)
```


# Purpose

In this vignette, we derive the entropy at the country level for different categories of topics.
Entropy describes how predictable a random variable $X$ with discrete probability mass function $P$ over $n$ outcomes is [@Shannon1948]:

\[ H(X) = - \sum_{i=1}^n P(x_i) log_b P(x_i)\]

In our case, $P(x_i)$ represents the topic probabilities outputted by the topic model.
In ecology, entropy is related to diversity through the Shannon-Wiener index.
Diversity is used interchangeably with entropy in this vignette and in the function naming.

# Data loading

We access the consolidated results stored in `extdata` using `system.file()`.

```{r}
general <- readRDS(system.file(
    "extdata",
    "consolidated_results_NSF_general.Rds",
    package = "wateReview")
)
specific <- readRDS(system.file(
    "extdata",
    "consolidated_results_NSF_specific.Rds",
    package = "wateReview")
)
methods <- readRDS(system.file(
    "extdata",
    "consolidated_results_methods.Rds",
    package = "wateReview")
)
budget <- readRDS(system.file(
    "extdata",
    "consolidated_results_water budget.Rds",
    package = "wateReview")
)
theme <-readRDS(system.file(
    "extdata",
    "consolidated_results_theme.Rds",
    package = "wateReview")
)
```

# Calculating diversity

First, we attach the `latinAmerica` and `dplyr` packages.

```{r, warning = FALSE, message = FALSE}
library(wateReview)
library(dplyr)
```

Then, we calculate the diversity by paper and for all of LAC using the `diversity_country()` function, largely dependent on `vegan::diversity()`.

```{r, warning = FALSE, message = FALSE}
relevant_documents <- remove_year_country(specific) #  specify which (species group)
diversity_LA <- diversity_LAC(relevant_documents)
diversity_paper <- vegan::diversity(relevant_documents)
general <- diversity_country(general)
specific <- diversity_country(specific)
budget <- diversity_country(budget)
diversity_by_country <- full_join(
    general, 
    full_join(specific, budget, by = "country"), 
    by = "country") %>%
   rename(general = x, specific = x.x, budget = x.y)
```

Here is the resulting table:

```{r}   
diversity_by_country %>% knitr::kable(digits = 3, align = "lccc", format = "html", caption = "Country entropy for general, specific and water budget topics") %>%
kableExtra::kable_styling(bootstrap_options = c("hover", "condensed"))
```

# Visualizing diversity with dot plots

To visualize the diversity, we attach some visualizations packages and prepare the data for visualization.

```{r}
library(ggplot2)
library(ggpubr)
library(ggrepel)
library(reshape2)
diversity_by_country_graph <- melt(diversity_by_country, id.vars = c("country"))
```

Now, let's visualize.

## Specific topics

```{r}
specific_graphdf <- subset(diversity_by_country_graph, variable == "specific")
specific_graph <- ggdotchart(specific_graphdf, x = "country", y = "value", #add color = cluster
                             add = "segments", sorting = "descending", rotate = TRUE, 
                             ylab = "Entropy across specific topics",
                             xlab = "Country")
specific_graph
```

## General topics

```{r}
general_graphdf <- subset(diversity_by_country_graph, variable == "general")
general_graph <- ggdotchart(general_graphdf, x = "country", y = "value", #add color = cluster
                            add = "segments", sorting = "descending", rotate = TRUE,
                            ylab = "Entropy across general topics",
                            xlab = "Country")
general_graph
```

## Water budget topics

```{r}
budget_graphdf <- subset(diversity_by_country_graph, variable == "budget")
budget_graph <- ggdotchart(budget_graphdf, x = "country", y = "value", #add color = cluster
                             add = "segments", sorting = "descending", rotate = TRUE,
                           ylab = "Entropy across water budget topics",
                           xlab = "Country")

budget_graph
```


```{r}
ggdotchart(diversity_by_country_graph, x = "country", y = "value", color = "variable",
           rotate = TRUE)

ggplot(diversity_by_country,aes(general, specific, label = country)) +
  geom_text_repel() +
  geom_point() +
  theme_pubr() +
  labs(x = "General topics",y = "Specific topics", title = "Country entropy")
```

# References