---
title: "Chord diagrams"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chord diagrams}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 12,
  fig.width = 12, 
  comment = "#>"
)
```


# Purpose


In this vignette, we produce a chord diagram representing the links of a weighted bi-partite network between countries and a category of topics.




# Getting the bi-partite network weighted adjacency matrix

We use the built-in function of the package, `get_network()`, to extract the weighted adjacency matrix.
We also load `magrittr` explicitely to access the `%>%` operator.

```{r libraries}
library(wateReview)
library(magrittr)
```

We select the specific topics with `type = "NSF_specific"`, indicate that the country membership are to be understood as probabilities with `prob = TRUE`.
The specific topics do not include methods, so we leave the default `filter_method = FALSE` which is useful for `type = "theme"`.
We display the default network with `blindspot = FALSE`, filter for countries with at least 30 documents with `country.threshold = 30` and filter the resulting matrix to retain only the weights above the 75th percentile with `percentile.threshold = .75`.


```{r get network}
weighted_adj_matrix <- get_network(type = "NSF_specific", prob = TRUE, filter_method = FALSE, blindspot = FALSE, country.threshold = 30, percentile.threshold = .75)
weighted_adj_matrix %>% 
	knitr::kable(digits = 3, format = "html", caption = "Bi-partite network weighted adjacency matrix") %>% 
	kableExtra::kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
	kableExtra::scroll_box(width = "7in")
```

# Chord diagram visualization

We can now use `VizSpots()` to display the chord diagram.
This function is largely using the `circlize` library which documentation can be found [here](https://jokergoo.github.io/circlize_book/book/).
`weighted_adj_matrix` is the matrix.
We ask for the non-scaled results with `scaled = FALSE`, add the socio-hydrologic clusters colors with `cluster_color = TRUE`, and re-order the countries so that they are grouped by clusters with `reorder_cluster = TRUE`.
We also add an outer ring identifying the general categories with `NSF_general_color = TRUE`.
We have to specify here again the topic category with `type = "NSF_specific"`.
Finally, `topic_threshold = .50` displays the topic which research volume in the corpus are above the 50th percentile.

```{r visualization}
VizSpots(weighted_adj_matrix, scaled = FALSE, cluster_color = TRUE, NSF_general_color = TRUE, type = "NSF_specific", topic_threshold = .50, reorder_cluster = TRUE)
```
