---
title: "Clustering analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Clustering analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 7,
  fig.width = 7, 
  comment = "#>"
)
```

# Purpose

In this vignette, we perform some quality control on the database of country socio-hydrologic descriptors.
After filtering, the data are examined with a correlation analysis and a clustering analysis.

```{r libraries}
library("wateReview")
library("ggplot2")
library("factoextra")
library("clValid")
```

# Loading data

```{r data_loading}
countries_shapefile <- join_database_shapefile(read_countries_database(), read_countries_shapefile())
att_names <- names(countries_shapefile)[-1]
```

# Visualizing attributes

```{r make_maps}
l.att_map <- lapply(names(countries_shapefile)[-1], make_map)
sample(l.att_map, 1)
```

```{r make_hists}
l.att_hist <- lapply(names(countries_shapefile)[-1], make_hist)
sample(l.att_hist, 1)
```

# QA/QC on country database

Let's rescale the data using the `make_corrmatrix` function with `rescale = TRUE`.
The `missmap()` function the `Amelia` package then displays the missing values in the resulting rescaled `data.frame`.

```{r data rescaling}
rescaled_data <- make_corrmatrix(corr_type = "spearman", rescale = TRUE, .plot = FALSE)  
rownames(rescaled_data) <- countries_shapefile$COUNTRY
Amelia::missmap(rescaled_data)
```

Some predictors are missing only in some countries.
We now try to identify the best set of predictors and countries by counting the number of `NA` with `count_nas()` and varying the threshold of number of `NA` per countries.

```{r optimum set of descriptors}
count_nas_col <- apply(rescaled_data, MARGIN = 2, FUN = count_nas) 
count_nas_row <- apply(rescaled_data, MARGIN = 1, FUN = count_nas) 
names(count_nas_row) <- countries_shapefile$COUNTRY
na_thresholds <- sort(unique(count_nas_row), decreasing = TRUE)
list_count_nas_col <- lapply(na_thresholds, function(na_threshold){
    filtered_data <- rescaled_data[count_nas_row <= na_threshold, ]
    current_count_nas_col <- apply(filtered_data, MARGIN = 2, FUN = count_nas) # columns
    return(current_count_nas_col)
})
count_nas_col_df <- do.call(cbind, list_count_nas_col)
list_country_left <- sapply(na_thresholds, function(na_threshold){
    filtered_data <- rescaled_data[count_nas_row <= na_threshold, ]
    return(nrow(filtered_data))
})
par(mfrow = c(2, 1))
oce::imagep(t(count_nas_col_df), col = oce::oce.colorsViridis(), decimate = FALSE, xlab = "NA threshold", ylab = "Country descriptors", main = "", cex = 1)
plot(list_country_left, xlab = "NA threshold", ylab = "Number of countries left")
```

Based on this visualization, we filter the country descriptors and drop the countries with missing values.
Notice that these removed countries correspond to Carribean nations.

```{r filtering data}
drops <- c("variability", "surface_withdrawl", "ground_withdrawl", "SPI..2017.", "SPI_basic_human", "SPI_found", "SPI_opp")
rescaled_data <- rescaled_data[, !colnames(rescaled_data) %in% drops]
count_nas_row <- apply(rescaled_data, MARGIN = 1, FUN = count_nas) # lines
rownames(rescaled_data) <- countries_shapefile$COUNTRY
# countries left
rownames(rescaled_data[count_nas_row <= 0, ])
# countries removed
setdiff(countries_shapefile$COUNTRY, rownames(rescaled_data[count_nas_row <= 0, ]))
filtered_data <- rescaled_data[count_nas_row <= 0, ]
Amelia::missmap(filtered_data)
```

# Correlation analysis

We can now calculate the correlations and distance matrices for all types of data.

## Pearson's correlations

```{r pearsons}
mat <- as.matrix(filtered_data)       
correlations <- Hmisc::rcorr(mat, type = "pearson")
correlations$r[which(correlations$P > 0.05)] <- 0
corrplot::corrplot(correlations$r, type = "upper")
```

## Spearman's correlations

```{r spearmans}
mat <- as.matrix(filtered_data)       
correlations <- Hmisc::rcorr(mat, type = "spearman")
correlations$r[which(correlations$P > 0.05)] <- 0
corrplot::corrplot(correlations$r, type = "upper")
```

## Distance matrices


```{r distance_matrix}
distance <- get_dist(filtered_data )
p_dist <- fviz_dist(distance, gradient = list(low = "steelblue",  high = "white"), order = TRUE)
p_dist
```

# Clustering analysis

Countries in the study area are clustered in relation with socio-hydrologic variables.
Two methods of clustering are used: $k$-means clustering [@Hartigan1979] and hierarchical clustering [@Murtagh1983].
The clustering is performed with Euclidian distances and following Ward's criterion.
The optimal number of clusters is investigated by evaluating the evolution with the number of clusters of the total within sums of square and of the average silhouette width [@Rousseeuw1987].
In addition, the following four validation metrics are used to assess the stability of the clustering under the complete set of clustering variables and a iterative procedure where one variable is removed from the set, an approach akin to leave-one-out cross-validation:

1. the average proportion of (APN) measures the proportion of observations not placed in the same cluster under both cases and evalutes how robust are the clusters under cross-validation [@Datta2003];
2. the average distance between means (ADM) measures the variation of the cluster center and evaluates the stability of the localization of the cluster in the multi-dimensional clustering variable space [@Datta2003];
3. average distance (AD) measures the distance between observations placed in the same cluster and evaluates within-cluster stability [@Datta2003];
4. the figure of merit (FOM) estimates the predictive power of the clustering algorithm by measuring the within-cluster variance of the removed variable [@Yeung2001].

Both clustering methods yield similar results.
The total within sum of squares exhibits a shift in the evolution of the total within sum of square after two clusters are chosen.
Similarly, the average silhouette width strongly exhibits a peak for two clusters.
Further inspection of clustering in PCA dimensions indicates that the cluster with Mexico and Brazil is significantly distinct from all other countries, explaining the observation of a sharp peak in average silhouette width.
However, validation metrics exhibits optimal null values of APN and ADM for two or three clusters.
In addition, AD and FOM are lower for three clusters than for two.
Based on this results, we chose three clusters to describe the grouping of countries based on their socio-hydrologic variables.


## Optimum clustering

We now derive the optimum clustering for $k$-means and hierarchical clustering.

###  $k$-means

```{r optimk_kmeans}
get_optimk(filtered_data, method = "kmeans")
```

### Hierarchical clustering

```{r optimk_hierarchical}
get_optimk(filtered_data, method = "hierarchical")
```


## Clustering stability

###  $k$-means

```{r clStab_kmeans}
cl_stability <- clStab(filtered_data, method = "kmeans")
stab <- cl_stability$stab
optim_df <- cl_stability$optim_df
summary(stab)
print("Optimal Number of Cluster under One Std Rule")
print(optim_df)
```

### Hierarchical clustering

```{r clStab_hierarchical}
cl_stability <- clStab(filtered_data, method = "hierarchical")
stab <- cl_stability$stab
optim_df <- cl_stability$optim_df
summary(stab)
print("Optimal Number of Cluster under One Std Rule")
print(optim_df)
```

## Cluster visualization

###  $k$-means

```{r pkms}
k2 <- kmeans(filtered_data, centers = 3, nstart = 25) 
fviz_cluster(k2, geom = "text",  data = filtered_data) + cowplot::theme_cowplot()
```

### Hierarchical clustering

```{r phcs}
res.hc <- eclust(filtered_data, "hclust", k = 3, graph = FALSE) 
fviz_dend(res.hc, rect = TRUE, show_labels = TRUE)
```

# References