---
title: "Hexagonal maps of country entropies"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Hexagonal maps of country entropies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 7,
  fig.width = 7, 
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# Purpose

This vignette visualizes the [country entropy](country_entropy.html).

# Libraries

```{r}
library(wateReview)
library(raster)
library(tmap)
library(geogrid)
library(RColorBrewer)
library(scales)
```

# Data loading

We read a `shapefile` of the region with the country long and short names, the information from the English topics and the [country entropy](country_entropy.html).
We then min-max rescale the data so that each entropy, $H$, is mapped following:

\[(0, \max H) \to (0,1)\]

These min-max rescaled data are assigned to the `shapefile`.

```{r}
LAC_map <- shapefile(system.file("extdata", "LAC_di.shp", package = "wateReview"))
LAC_map@data <- subset(LAC_map@data, select = c("COUNTRY", "NAME"))
topics <- read.csv(system.file("extdata", "topic_names_en.csv", package = "wateReview"))
entropy_data <- read.csv(system.file("extdata", "diversity.csv", package = "wateReview"))
entropy_data$NSFgeneral <- scales::rescale(
  entropy_data$NSFgeneral, 
  to = c(0, 1), 
  from = c(0,  log(length(unique(topics$NSF_general)))))
entropy_data$NSFspecific <- scales::rescale(
  entropy_data$NSFspecific, 
  to = c(0, 1), 
  from = c(0,  log(length(unique(topics$NSF_specific)))))
entropy_data$budget <- scales::rescale(
  entropy_data$budget, 
  to = c(0, 1), 
  from = c(0,  log(nrow(topics[topics$description == "methods", ]))))
LAC_map <- LAC_map[LAC_map$COUNTRY %in% entropy_data$country, ]
LAC_map@data <- merge(LAC_map@data, entropy_data,  by.x= "COUNTRY", by.y = "country")
```

# Non-hexagonal map

```{r}
tm_shape(LAC_map) +
  tm_polygons("NSFgeneral", style = "cont", palette = "Blues") +
  tmap_options(max.categories = 50) +
  tm_text("NAME")
```

# Generating hexagons

We use here the package `geogrid`.

```{r}
LAC_hex <- assign_polygons(LAC_map, calculate_grid(shape = LAC_map, grid_type = "hexagonal", seed = 5))
```

# Hexagonal maps

## General topics

```{r}
pal <- "Blues"
brk <- seq(.5, 1, by = .1)
tm_shape(LAC_hex) + 
  tm_polygons("NSFgeneral", style = "cont", breaks = brk, palette = pal) + 
  tm_text("NAME")
```

## Specific topics

```{r}
tm_shape(LAC_hex) + 
  tm_polygons("NSFspecific", style = "cont", breaks = brk, palette = pal) + 
  tm_text("NAME")
```

## Water budget topics

```{r}
tm_shape(LAC_hex) + 
  tm_polygons("budget", style = "cont", breaks = brk, palette = pal) + 
  tm_text("NAME")
```

This maps can these easily be modified with a vector drawing software.