---
title: "LDA comparison"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LDA comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 7,
  fig.width = 7, 
  comment = "#>"
)
```

# Purpose

In this vignette, we compare the topics outputted by topic modelling on three different corpora in English, Spanish and Porturguese.

# Data loading

We access the topic lists stored in `extdata` using `system.file()`.

```{r, warning = FALSE, message = FALSE}
library(dplyr)
library(reshape2)
en <- read.csv(system.file(
    "extdata",
    "topic_names_en.csv",
    package = "wateReview")
) %>% mutate(lang = "en") %>% melt(id.vars = c("topic_id","lang"))
es <- read.csv(system.file(
    "extdata",
    "topic_names_es.csv",
    package = "wateReview")
) %>% mutate(lang = "es") %>% melt(id.vars = c("topic_id","lang"))
pt <- read.csv(system.file(
    "extdata",
    "topic_names_pt.csv",
    package = "wateReview"),
    na.strings=c("","NA")
) %>% mutate(lang = "pt") %>% melt(id.vars = c("topic_id","lang"))
```

Each of these language data.frame holds the `topic_id` outputted by the topic model and a language identifier `lang`.
`variable` holds the category of topics: general, specific, water budget, methods and theme and `value` the corresponding topic name.

```{r}
head(en %>% filter(variable == "NSF_specific"))
```

We know bind the three language data.frames, filter for the specific topics and count their occurence across themes per topic and language.

```{r}
lda_comparison <- rbind(en, es, pt) %>% na.omit() %>%
  filter(variable == "NSF_specific") %>%
  group_by(value, lang) %>%
  tally()
head(lda_comparison)
```


To compare Spanish and Portuguese results with the English ones, we need to re-order the data.frame based on the tally of the English results and the overall number of covered topics.

```{r}
lda_comparison$nlang <- lda_comparison %>% 
  group_by(value) %>% 
  group_map(~ rep(length(table(.x$lang)), length(table(.x$lang)))) %>% 
  unlist()
lvls <- as.character(lda_comparison$value[lda_comparison$lang=="en"])[order(lda_comparison$n[lda_comparison$lang=="en"])]
lda_comparison$value <- factor(lda_comparison$value, levels = lvls)
lda_comparison <- na.omit(lda_comparison) # missing 1 spanish?
lda_comparison$lang <- factor(lda_comparison$lang, labels = c("English", "Spanish", "Portuguese"))
```

# Visualization

We now load some visualization libraries and presents the comparison as a heatmap where the number corresponds to the number of raw LDA topics and the color to the coverage between the three languages.

```{r, warning = FALSE, message = FALSE}
library(ggplot2)
library(forcats)
library(ggpubr)
ggplot(data = lda_comparison, aes(x = lang, y = fct_reorder(value, nlang))) +
  geom_tile(aes(fill = nlang, width=0.9, height=0.9)) +
  geom_text(aes(label = n)) +
  scale_fill_gradient(low = "grey89",
                      high = "grey50") +
  labs(title= "Topic model coverage",
       y="NSF specific categories",
       x = "Topic model for each language") +
  theme_pubr() +  
  theme(axis.text.y = element_text(face = c('plain','plain','plain', 'plain', 'plain', 'plain', 'plain',
                                            'plain', 'bold', 'plain', 'plain', 'plain',
                                            'plain', 'plain', 'plain', 'bold', 'plain',
                                            'plain', 'plain', 'plain', 'plain', 'plain',
                                            'plain', 'bold', 'plain', 'plain', 'bold',
                                            'bold', 'bold', 'plain', 'plain', 'bold', 
                                            'bold', 'plain', 'bold','bold', 'bold', # 6-10
                                            'bold', 'bold', 'bold','bold','bold' # 1-5
                                            ))) +
  rremove("legend")
```