---
title: "Normality"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Normality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 6,
  fig.width = 6, 
  comment = "#>"
)
```

# Purpose

In this vignette, we derive the _normality_ of five categories of topics.
Normality from the Jensen-Shannon distance, $d_{JS}$, [@Endres2003], defined as the square-root of the Jensen-Shannon divergence, $D_{JS}$, [@Lin1991]:

\[ D_{JS}(N,Q) = \frac{1}{2} \lbrack D_{KL}(N,R) + D_{KL}(P,R) \rbrack \] 

with $N,P$, probability distributions, $R = \frac{1}{2} (N+P)$ the midpoint probability and $D_{KL}$, the Kullback-Leibler divergence [@Kullback1951].
Here, we take $N = \mathcal{N}(0,1)$, the standard normal distribution with mean $\mu = 0$ and standard deviation $\sigma = 1$.
As $d_{JS} = 0$ when $P = \mathcal{N}(0,1)$, to better meet the intuition of normality, we define normality as:

\[ \textrm{Normality} = 1 - d_{JS} \]

so that normality is closer to 1 when the $P$ is closer to the standard normal distribution.

For a given topic, normality is defined for two types of distributions $P$, forming the two axis of subsequent graphs:

1. the probability distribution of the percentage of research devoted to the topic across countries;
1. the probability distribution of topic probabilities across documents.

# Data loading

We access the consolidated results stored in `extdata` using `system.file()`.

```{r}
general <- readRDS(system.file(
    "extdata",
    "consolidated_results_NSF_general.Rds",
    package = "wateReview")
)
specific <- readRDS(system.file(
    "extdata",
    "consolidated_results_NSF_specific.Rds",
    package = "wateReview")
)
methods <- readRDS(system.file(
    "extdata",
    "consolidated_results_methods.Rds",
    package = "wateReview")
)
budget <- readRDS(system.file(
    "extdata",
    "consolidated_results_water budget.Rds",
    package = "wateReview")
)
theme <- readRDS(system.file(
    "extdata",
    "consolidated_results_theme.Rds",
    package = "wateReview")
)
```

# Deriving normality

First, we select the countries with at least 30 documents to keep the stastitics tidy.

```{r libraries}
library(wateReview)
```

Next, we calculate the normality across countries and topics for the five categories with:

```{r, message = FALSE, warning = FALSE}
topic_categories <- list(general, specific, methods, budget, theme)
distances <- lapply(topic_categories, function(category){
  probs <- reduce_docs_for_JSd(category)
  country_distance <- get_country_distance(probs)
  topic_distance <- get_topic_distance(probs)
  return(merge(country_distance, topic_distance, by = "topic"))
})
```

# Visualizations

Let's load some plotting libraries and create the base plots.

```{r, message = FALSE, warning = FALSE}
library(ggplot2)
library(ggpubr)
library(plotly)
normality_plots <- lapply(distances, function(category_distance){
  ggplot(category_distance, aes(topic_distance, country_distance, label = topic)) +
  geom_point() +
  theme_pubr() +
  coord_fixed() +
  labs(x = "Normality across documents",y = "Normality across countries")
})
```

Now, we adjust the base plots according to each category.

## General

```{r}
ggplotly(
  normality_plots[[1]] + labs(title = "General topics"),
  tooltip = c('topic')
  )
```

## Specific

```{r}
ggplotly(
  normality_plots[[2]] + labs(title = "Specific  topics"),
  tooltip = c('topic')
  )
```

## Methods

```{r}
ggplotly(
  normality_plots[[3]] + ylim(0.5,0.93) + xlim(0.26,0.67) + labs(title = "Research methods"),
  tooltip = c('topic')
  )
```

## Budget


```{r}
ggplotly(
  normality_plots[[4]] + ylim(0.5,0.93) + xlim(0.26,0.67) + labs(title = "Components of water budget"),
  tooltip = c('topic')
  )
```

## Themes

```{r}
ggplotly(
  normality_plots[[5]] + labs(title = "Themes"),
  tooltip = c('topic')
  )
```

# References