---
title: "Query Q&A"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Query Q&A}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 9,
  fig.width = 9, 
  comment = "#>"
)
```

# Purpose

This vignette presents the QA/QC of the query process.

# Libraries

```{r, message = FALSE, warning = FALSE}
library(wateReview)
library(ggplot2)
library(dplyr)
```

# Data loading

We load the initial and final query and corpus databases.

```{r}
load(file = system.file("extdata", "language_dfs.rda", package = "wateReview"))
initial_meta_df <- get_meta_df(language_dfs)
load(file = system.file("extdata", "language_dfs_updated_3.rda", package = "wateReview"))
final_meta_df <- get_meta_df(language_dfs)
head(final_meta_df, 3) %>%
	knitr::kable(digits = 3, format = "html", caption = "") %>% 
	kableExtra::kable_styling(bootstrap_options = c("hover", "condensed")) %>% 
	kableExtra::scroll_box(width = "7in")
```

We use `query_QA_plots()` to produce all plots.

```{r}
initial <- query_QA_plots(initial_meta_df)
final <- query_QA_plots(final_meta_df)
```

# Sources

## English (initial vs final)

### Initial

```{r, echo = FALSE}
initial$source$english
initial$source_DOI$english
```

### Final

```{r, echo = FALSE}
final$source$english
final$source_DOI$english
```

## Spanish (initial vs final)

### Initial

```{r, echo = FALSE}
initial$source$spanish
initial$source_DOI$spanish
```

### Final

```{r, echo = FALSE}
final$source$spanish
final$source_DOI$spanish
```

## Portuguese (initial vs final)

### Initial

```{r, echo = FALSE}
initial$source$portuguese
initial$source_DOI$portuguese
```

### Final

```{r, echo = FALSE}
final$source$portuguese
final$source_DOI$portuguese
```

# Time coverage

## Initial

```{r, echo = FALSE}
initial$time_histogram
initial$time_density
```

## Final

```{r, echo = FALSE}
final$time_histogram
final$time_density
```

# Citations

## Initial

```{r, echo = FALSE}
initial$citations
```

## Final

```{r, echo = FALSE}
final$citations
```