---
title: "Timelines"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Timelines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 7,
  fig.width = 7, 
  comment = "#>"
)
```

# Purpose

This vignette presents the research growth through time.

# Libraries

```{r libraries, warning = FALSE, message = FALSE}
library(wateReview)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(plotly)
```

# Data loading

We load the consolidated results for the entire corpus which contains the general topics caterogy and the predicted country. 

```{r data loading}
documents_year_location <- readRDS(system.file("extdata", "consolidated_results_NSF_general.Rds", package = "wateReview")) %>%
  select(c(year, country)) %>%
  filter(country != "Irrelevant") %>%
  mutate(country = as.character(country))
dim(documents_year_location)
head(documents_year_location)
```

We group the country by [clusters](clustering_analysis.html). 
We define a convenience function to do so which assign the country cluster to `country` and take care of removing the the Carribean countries which were not clustered.

```{r}
assign_cluster <- function(country){
  cluster1 <- c("Mexico", "Brazil")
  cluster2 <- c("Chile", "Argentina", "Uruguay", "Suriname", "Guyana", "Belize", "Paraguay", "Costa.Rica", "Cuba", "Panama", "Venezuela")
  cluster3 <- c("Colombia", "Bolivia", "Jamaica", "Nicaragua", "El.Salvador", "Ecuador", "Honduras", "Guatemala", "Peru", "Dominican Republic")
  if (country %in% cluster1){
    return(1)
  } else if (country %in% cluster2){
    return(2)
  } else if (country %in% cluster3){
    return(3)
  } else {
    return(NA)
  }
}
documents_year_location <- documents_year_location %>%
  mutate(cluster = sapply(country, assign_cluster)) %>% 
  na.omit()
dim(documents_year_location)
head(documents_year_location)
```

# Counting documents per year per cluster

```{r}
count_year_cluster <- documents_year_location %>%
  select(-country) %>%
  group_by(cluster) %>%
  group_modify(~ table(.) %>% t() %>% as.data.frame()) %>%
  select(- Var1) %>%
  rename(year = ".", count = Freq) %>%
  mutate(cluster = as.factor(cluster), year = as.numeric(as.character(year))) %>%
  filter(year >= 2000) %>%
  filter(year < 2018) %>%
  tidyr::complete(year = tidyr::full_seq(year, period = 1))
 count_year_cluster$count[is.na(count_year_cluster$count)] <- 0 
head(count_year_cluster)
```

# Visualizing growth through time

```{r, warning = FALSE, message = FALSE}

growth <- ggplot(count_year_cluster, aes(x = year, y = count, fill = cluster)) +
  theme_pubr(legend = "none") +
  geom_area(alpha = 0.6 , size =.5, colour = "white") +
  scale_fill_manual(
    values = c("#F8766D", "#00BFC4", "#7CAE00"),
    labels = c("Cluster 1", "Cluster 2", "Cluster 3")
    ) +
  scale_x_continuous(
    minor_breaks = seq(1980, 2020, by = 1), 
    breaks = seq(1980, 2020, by = 5)
    ) +
  theme(
    axis.title.x = element_blank(), 
    plot.title = element_text(hjust = 0.5),
    legend.title=element_blank()
    ) +
  labs(y = "New water resources articles", x = "Time")
ggplotly(growth)  
```

# Residual analysis

Recognizing an exponential growth, we perform a residual analysis by fitting an exponential curve to the general trend per cluster and evaluating the deviation from this general trend.
We additionally flag if the residuals absolute values are greater than one-standard deviation of the residuals.

```{r}
residual_year_cluster <- count_year_cluster %>%
  group_modify( ~ data.frame(
    year = .x$year, 
    resid = lm(log(count + 1) ~ year, data = .x) %>% resid()
    ) %>%
  mutate(signif = resid > 0) %>%
  mutate(signif = ifelse(abs(resid) < sd(resid), NA, signif))
  )
residual_year_cluster
```

```{r}
plot_fun <- function(.x, .title = .y$cluster){
  p <- ggplot(.x) + 
    aes(x = year, y = resid, color = resid > 0, fill = signif) +
    theme_pubr(legend = "none") +
    scale_fill_manual(values = c("black","black")) +
    scale_color_manual(values = c("grey20","grey20")) +
    geom_hline(yintercept = sd(.x$resid), linetype="dashed", color="grey50") +
    geom_hline(yintercept = -sd(.x$resid), linetype="dashed", color="grey50") +
    labs(title = .title, y="Growth trend residuals") +
    theme(plot.title = element_text(hjust = 0.5)) +
    ylim(-.5, .5) +
    geom_bar(stat = "identity") +
    theme(axis.title.x = element_blank(), legend.position = "none") +
    scale_x_continuous(minor_breaks = seq(1980, 2020, by=1), breaks = seq(1980, 2020, 5)) +
    theme(panel.grid.major.x = element_line(size = .3, linetype = "solid", color = "grey62"))
    return(p)
}
residual_year_cluster %>% group_map(~  plot_fun(.x, .title = paste("Cluster", .y$cluster)))
```